Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-20 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
example looked at. but needs actual data

@@

\section{Example}

@@

Using the previously described techniques, we have implemented a system capable of performing an inference similar to the one presented in Figure \ref{fig:example}. The base and target cases are created by running the Dora system on the two different simulated classroom worlds shown in Figure~\ref{fig:dora-maps}. In each case, Dora is manually driven around the room to allow it to create metric and place maps. Once the map is created, Dora is then driven in front of each object and the visual recognition system is run, resulting in the objects being added to the place layer.

The data from Dora's spatial model is then passed on to the qualitative spatial representation generator. In the base case, there are 16 desks and a chalkboard. There are two other entities in the case: the room area and the context-specific spatial region representing the front of the room. The case includes a total of 96 expressions relating the 19 entities. Nine of these expressions are used to define the boundary of a context-specific spatial region representing the front of the room: the four desks in the front row, the chalkboard, and the leftmost bottom and leftmost top of the room. The target case includes only 12 desks arranged in three columns of four, a chalkboard and a lectern. The target case includes 73 statements and 14 entities.

SME generates an analogy between the base and target cases enabling the transfer of the symbolic description of the front of the room to the new situation. The resulting analogy includes 62 correspondences between the entities and expressions in the base and target and 53 candidate inferences.  All seven \fw{regionBoundary} statements in the base appear as candidate inferences. Five of the anchor points are exactly correct, the leftmost corners of the room, the chalkboard and two of the desks in the front row. The other two analogically transferred anchor points are to the lectern and a desk in the third row. Figure \ref{fig:success} illustrates the region created by the seven boundary points in the target environment. While this region is not identical to how a human would specify it, our system is able to produce a fairly accurate context-dependent spatial region in a new environment from a single example.

@@

\section{Limitations of Initial Approach}

The spatial transfer algorithm described in here has a number of limitations to be addressed in future work.  First, we have not incorporated a memory retrieval mechanism, such as MAC/FAC \cite{forbus/etal1995}.  As a cognitive system gains experience in different environments, it will have access to a range of context-dependent spatial regions defined in a variety of task situations. To retrieve an analogous example, the agent must select the most similar environment that contains a labeled example of the sought after region type. This extension is fairly straightforward, but beyond the scope of this paper. Second, our initial approach ignores a number of potentially relevant pieces of information. After the context-dependent spatial region has been identified in the target environment, its qualitative spatial relationships could be compared with those from the base to either refine the region or provide a confidence measure for the inference. In our example, the transferred region contains the bottom desk in the second row, but the corresponding region does not contain any desks topologically. Third, our algorithm uses an absolute reference frame. Therefore, the environments must be oriented in a similar fashion to successfully transfer a context-dependent spatial region. We can overcome this limitation by performing a series of analogies between the base and the target in which we rotate the base and select the analogy with the best mapping. Finally, more advanced qualitative spatial relationships should improve performance. For example, recognizing all the desks as one region, or grouping them into rows or columns, would provide a better level of abstraction for this task.

>>>>

\from{Nick}{This section feels a bit long. Can we cut it down at all? Perhaps the second half of the second paragraph if we don't use the constraints explicitly}

@@

\section{Example System Run}\label{sec:example}

@@

\from{Nick}{I'd like to keep an example like this in the paper, but we need to choose carefully so we can minimise the number of space-consuming images we need}

To elucidate the workings of our system, we now present an example of how it can transfer a CDSR describing the front of a known classroom (the base) to a new classroom (the target).

We first create the base and target representations by running Dora in the two different classrooms \textbf{TODO:image+ref here}. In each case, Dora is manually driven around the room to allow it to create a metric map. Once the map is created, Dora is then positioned such that the objects are observable and the visual recognition system is run. The map and object data that results from this is then passed on to the QSR generator. \from{Nick}{TODO: update for actual example} In the base case, there are 16 desks and a chalkboard. There are two other entities in the case: the room area and the CDSR representing the front of the room. The case includes a total of 96 expressions relating the 19 entities. Nine of these expressions are used to define the boundary of a CDSR representing the front of the room: the four desks in the front row, the chalkboard, and the leftmost bottom and leftmost top of the room. The target case includes only 12 desks arranged in three columns of four, a chalkboard and a lectern. The target case includes 73 statements and 14 entities.

SME generates an analogy between the base and target cases enabling the transfer of the symbolic description of the front of the room to the new situation. The resulting analogy includes 62 correspondences between the entities and expressions in the base and target and 53 candidate inferences.  All seven \fw{regionBoundary} statements in the base appear as candidate inferences. Five of the anchor points are exactly correct, the leftmost corners of the room, the chalkboard and two of the desks in the front row. The other two analogically transferred anchor points are to the lectern and a desk in the third row. Figure \ref{fig:success} illustrates the region created by the seven boundary points in the target environment.

% While this region is not identical to how a human would specify it, our system is able to produce a fairly accurate context-dependent spatial region in a new environment from a single example.

@@

% We can put back in if desired
%
% \section{Limitations of Initial Approach}
% 
% The spatial transfer algorithm described in here has a number of limitations to be addressed in future work.  First, we have not incorporated a memory retrieval mechanism, such as MAC/FAC \cite{forbus/etal1995}.  As a cognitive system gains experience in different environments, it will have access to a range of context-dependent spatial regions defined in a variety of task situations. To retrieve an analogous example, the agent must select the most similar environment that contains a labeled example of the sought after region type. This extension is fairly straightforward, but beyond the scope of this paper. Second, our initial approach ignores a number of potentially relevant pieces of information. After the context-dependent spatial region has been identified in the target environment, its qualitative spatial relationships could be compared with those from the base to either refine the region or provide a confidence measure for the inference. In our example, the transferred region contains the bottom desk in the second row, but the corresponding region does not contain any desks topologically. Third, our algorithm uses an absolute reference frame. Therefore, the environments must be oriented in a similar fashion to successfully transfer a context-dependent spatial region. We can overcome this limitation by performing a series of analogies between the base and the target in which we rotate the base and select the analogy with the best mapping. Finally, more advanced qualitative spatial relationships should improve performance. For example, recognizing all the desks as one region, or grouping them into rows or columns, would provide a better level of abstraction for this task.
